---
name: Julian 
surname: Garcia
position: "Student"
address: "1745 River Road Modesto CA"
phone: +1 209 918 1492
email: "garcia_julian94@yahoo.com"
github: JulianGarcia00
aboutme: "Veterinary Technician pursuing Veterinary School."
header-includes:
   - \usepackage{multicol}
   - \usepackage{setspace}
headcolor: 414141
output: 
  vitae::awesomecv:
    page_total: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library (here)
library(tidyverse)
```

# Education
```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "AS in Biological Sciences", "Modesto Junior College", "Modesto, CA", "2018", 
  
  "AA in Biological Sciences", "Modesto Junior College", "Modesto, CA", "2018", 
  
  "BS in Biological Sciences", "California State University, Stanislaus", "Turlock, CA", "2025", 
  
  "Minor in Chemistry ", "California State University, Stanislaus", "Turlock, CA", "2025", 
    
) %>% 
detailed_entries(degree, dates, uni, loc)
```

# Professional Positions
```{r professional}
tribble(
    ~ role, ~ company, ~ loc, ~ dates,
  "Veterinary Technician", "Standiford Veterinary Center", "Modesto, CA", "04/2022-Present",
 
) %>% 
  detailed_entries(company, dates, role, loc)
```

<!-- # Publications Section -->

# Peer-Reviewed Publications

\setlength{\leftskip}{0cm}
\textbf{2025}

\setlength{\leftskip}{1cm}
\begin{footnotesize}
\{Azevedo, L.}, \textbf{Garcia, J.}, \{Garcia, P.}, & \{Hedley, T.} (2025). Elizabethkingia miricola \textit{Elizabethkingia}. Microbiology Resource Announcements.
\end{footnotesize}

\setlength{\leftskip}{1cm}
\begin{footnotesize}
\textbf{Garcia, J.} (2025). DKA and GPR4. CSU Journal of Biochemistry.  
\end{footnotesize}


\setlength{\leftskip}{0cm}


# Honors and Awards

California State
```{r}
tribble(
  ~ award, ~ year,
  "Cum Laude", "2025",
  "Deans List", "2023-2025"
) %>%
  brief_entries(award, year)
```


# Outreach and Service
\begin{footnotesize}
Stanislaus State
\begin{itemize}
\item Pre-vet club Treasurer (2024-Present)
\item Science in Our Community (2023-present)
\end{itemize}